Exploratory Plots

### 2020-06-10 exploratory/2020/README.Rmd
Use manual colors

### Performance as measured by runtime
```{r fit_db_benchmarks, warning=FALSE}
benchmarks <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/benchmarks.tsv')) %>%
  relevel_method
benchmarks %>%
  group_by(dataset, method) %>%
  ggplot(aes(x = method, y = s, color = dataset)) +
  geom_boxplot() +
  scale_color_brewer(palette = "Dark2") +
  #scale_color_manual(values = dataset_colors) +  # bug in geom_boxplot with manual colors?
  facet_wrap("ref") +
  labs(y = 'seconds')
```

>>>>

### Performance as measured by runtime
```{r fit_db_benchmarks, warning=FALSE}
benchmarks <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/benchmarks.tsv')) %>%
  relevel_method
benchmarks %>%
  group_by(dataset, method) %>%
  ggplot(aes(x = method, y = s, color = dataset)) +
  geom_boxplot() +
  scale_color_manual(values = dataset_colors) +  
  facet_wrap("ref") +
  labs(y = 'seconds')
```
